MS797 Glossary

### 2022-02-10 _academics/ms797-glossary/ms797-glossary.Rmd
Add correlation formula LaTeX

correlation (70)
: a measure of the linearity of the relationship between $X$ and $Y$; values close to 0 indicate weak-to-no relationship, values near 1 or -1 indicate strong positive or negative correlation
(horrible formula on p.70 I don't have time to LaTeX at the moment)

>>>>

correlation (70)
: a measure of the linearity of the relationship between $X$ and $Y$; values close to 0 indicate weak-to-no relationship, values near 1 or -1 indicate strong positive or negative correlation
$$\text{Cor(X, Y)} = {\frac {\sum _{i=1}^{n}(x_{i}-{\bar {x}})(y_{i}-{\bar {y}})}{{\sqrt {\sum _{i=1}^{n}(x_{i}-{\bar {x}})^{2}}}{\sqrt {\sum _{i=1}^{n}(y_{i}-{\bar {y}})^{2}}}}}$$
